### 2013-04-09 exam6/2.tex
fix prob 3

\newpage
\item

@@

>>>>

\begin{solution}
\begin{verbatim}
// This class is an example
class Count implements Computation<Integer> {
    Integer i;
    Count() {
        this.i = 0;
    }

    public Integer run() {
        Integer j = this.i;
        this.i = i+1;
        return j;
    }      
}
\end{verbatim}
\newpage
\begin{verbatim}
// 6 pts total
// 2 pt class structure
class Repeat implements Computation<ArrayList<Integer>> {
    Computation<Integer> comp;
    Integer n;
    Repeat(Computation<Integer> comp, Integer n) {
        this.comp = comp; this.n = n;
    }

// 2 pts for run
    public ArrayList<Integer> run() {
        ArrayList<Integer> as = new ArrayList<Integer>();
        for(int i = 0; i < n; i++) 
          as.add(comp.run());
        return as;
    }      
}
// 2 pt for tests (need an example Computation<Integer>)
t.checkExpect((new Repeat(new Count(3))).run, new ArrayList(0,1,2));
\end{verbatim}
\newpage
\end{solution}

\item

@@

\begin{solution}
\newpage
\begin{verbatim}
// 2 pt structure (including purpose etc)
class Thunk<X> implements Computation<X> {
    Delay<X> s;
    Thunk(Computation<X> c) {
        this.s = new Frozen<X>(c);
    }
// 1 pts 
    public X run() {
        this.s = this.s.force();
        return this.s.val();
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 7 pts for the code in general, may have different design
interface Delay<X> {
    Delay<X> force();
    X val();
}
class Frozen<X> implements Delay<X> {
    Computation<X> c;
    Frozen(Computation<X> c) {
        this.c = c;
    }
    public Delay<X> force() {
        return new Thaw<X>(this.c.run());
    }
    public X val() {
        return null;
    }
}
class Thaw<X> implements Delay<X> {
    X x;
    Thaw(X x) {
        this.x = x;
    }
    public Delay<X> force() {
        return this;
    }
    public X val() {
        return this.x;
    }
}
\end{verbatim}
\newpage
\begin{verbatim}
// 2 pts tests
class Examples {
    void testThunk(Tester t) {
        Computation<Integer> count = new Count();
        t.checkExpect(count.run(), 0);
        t.checkExpect(count.run(), 1);
        t.checkExpect(count.run(), 2);
        t.checkExpect(count.run(), 3);
        Computation<Integer> thunk = new Thunk<Integer>(new Count());
        t.checkExpect(thunk.run(), 0);
        t.checkExpect(thunk.run(), 0);
    }

}
\end{verbatim}
\end{solution}
